



```{r}
library(tidyverse)
library(googlesheets)
library(rmapshaper)
library(rvest)
library(sf)
library(sp)
library(GADMTools)
```

```{r}
my_sf <- st_read("gadm36_ZAF_shp/gadm36_ZAF_1.shp")
```




prov <- c("Free State", "Gauteng", "Western Cape", "Northern Cape", "Mpumalanga", "KwaZulu-Natal", "Eastern Cape", "Limpopo")



```{r}
#sa_wrapper = gadm_sf.loadCountries("ZAF", level = 1, basefile = "./")

my_spdf = as(my_sf, "Spatial")
class(my_spdf)

str(my_spdf, max.level = 2)

glimpse(my_spdf@data)
```


```{r}

sa_sf = st_as_sf(my_spdf)
class(sa_sf)
```


```{r}
head(sa_sf, 4)
```

```{r}
glimpse(sa_sf)
```

```{r}
x <- readRDS("ZAF_adm1.sf.rds")

```

```{r}
library(rmapshaper)
simp_sf <- ms_simplify(sa_sf, keep = 0.01, keep_shapes = TRUE)
simple_geometry <- st_geometry(simp_sf)

plot(simple_geometry, main = "South Africa")
```

```{r}
library(ggplot2)
library(sf)
library(rnaturalearth)
library(units)
library(lwgeom)
library(dplyr)


attributes_df <- readRDS('attributes.rds')

sa_sf1 <- sa_sf1 %>%
  rename(
    prov = NAME_1
  )

sa_sf1 <- sa_sf1 %>%
  left_join(attributes_df, by = 'prov')



```

```{r}
sa_attributes <- saveRDS(sa_sf, "sa_attributes.rds")
```

```{r}

simp_sa_sf <- ms_simplify(sa_sf, keep = 0.01, keep_shapes = TRUE)

saveRDS(simp_sa_sf, "sa_attributes.rds")


```

```{r}
library(tidyverse)
library(sf)


plot(sa_sf["pop_2011.x"])


```

```{r}
library(tmap)
sa_sf %>%
  tm_shape() +
  tm_fill(col = "pop_2011.x", title = "No. People") + 
  tm_borders(lwd = 0.1) +
  tm_text("prov", size = 0.5) +
  tm_style("gray") +
  tm_layout(
    main.title = "Population (2011)",
    main.title.position = c("center"),
    main.title.size = 1,
    legend.position = c("right", "bottom")
  ) +
  tm_credits("Data:\n2011 Census", position = c("left", "bottom"))
```

```{r}
sa_sf_shiny <- saveRDS(sa_sf, "attributes_shiny.rds")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

ind_sf <- ind_sf %>%
  mutate(my_area = as.vector(my_area), 
         gdp_density_usd_km2 = as.vector(gdp_density_usd_km2))

original_geometry <- st_geometry(ind_sf)

library(rmapshaper)
simp_sf <- ms_simplify(ind_sf, keep = 0.01, keep_shapes = TRUE)
simple_geometry <- st_geometry(simp_sf)

par(mfrow = c(1,2))
plot(original_geometry, main = "Original Geometry")
plot(simple_geometry, main = "Simple Geometry")


